\section *{\LARGE 5. MARKETING PLAN }
\section *{Our marketing plans to launch our app are: }
\begin{itemize}
    \item  WRITE A BLOG:By writing a blog related to our application, we tell our audience about the development process. Blogging can build interest around our product and provides better search visibility to the user. Select target keywords, create quality content, and link to influence-rs to improve our blog’s search engine rankings.
    \item CREATE YOUTUBE VIDEO:Humans are visual creatures, which is why videos are the most popular form of content today. We can create video for YouTube as it’s a powerful tool to spread the word about your product. An effective way to market an app is to create a fun video using famous heroes or playing on sensational memes.
    If we want to create a promo video, keep it short and to the point, focus only on our app’s best features and provide a strong call to action. As a final check, mute our video. If it still makes sense, it’s well done..
    \item REACH OUR AUDIENCE WITH SOCIAL NETWORKS:Social media can help us to reach our potential customers more easily. Social networks provide us an access to important data about users’ interests, hobbies, and so on. This information can help businesses to target their advertisements. For example, Facebook Ads allows us to customize advertising as accurately as possible since ads are targeted solely at our potential users.
    \item PERFORM COMPETITOR RESEARCH: Knowing about our competitors will help us to communicate with our target audience, distinguish our business from competitors, improve our processes, and navigate challenges in our market. Determine their main advantages and try to improve on them.
\end{itemize}
