\section *{\LARGE ABSTRACT}
In the third semester of our program we have a course of developing a Capstone II project. We have to choose a topic which can solve a real-life problem and develop an application out of it.So, the topic we have chosen is Corona Safe an app which provide all the latest information about corona and screening tool option to check whether you are affected by COVID-19 or not.
This capstone II project is an application that enables the public to know whether they are positive or negative for the Corona virus. This capstone project is the part of the Mobile Application Design and Development course in third semester at Lambton College. This application was created by Sanjeev Gupta and Rajwinder Kaur and is referred to as “Corona Safe”. Currently, there are a few applications in the market such as “Corona, CA” and “Test Yourself Puducherry”. However, these applications do not provide the latest news about the Corona virus as well as an easy format to follow for children and adults. This indicates the need for this application in the market and the challenge this application brings. 
This is the specification report which include all the information of the project. This report explains the idea of the project, what are the requirement will be full filled and technical requirements with clear diagram and also explained the API which will be used to create the project. This also consist the Mock-up which por- trays the basic idea of project and how much time we will work on each task and how to and when we will finish it, this information is clearly explained in the Giant Chart.
